Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$

### 2016-04-25 paper/ms.tex
corner_plot.py updated to take only objects with logM>9.8. Little changes in ms.tex

We use halo catalogs constructed with a Bound-Density-Maxima (BDM)
algorithm. 
The catalogs were obtained from the publicly available Multidark
database  \footnote{\url{http://www.multidark.org/MultiDark/}}
\citep{MultiDark}. 
For each  halo in the box we extract its comoving position and mass.  
We focus our work on halos more massive than $1.5\times
10^{9}$\hMsun\ resolved with at least  $10$ particles. 
We do not take into account sub-halos.

@@

The MCMC exploration is done using a total of 24 seeds and 400
iterations (9600 models) to sample the posterior  probability distribution function 
($P(\mathcal{M}|\mathrm{observations}$) based on the Angular
Correlation Function (ACF). We put a flat prior on $\log M_{\rm min}$ and $\log \mmax$ between
$9.2$ up to $13.4$, corresponding to the halo mass range of
the simulation at $z=3$.
We restrict the selection to models that give a minimal number density
$N_{\rm{halos}}>N_{\rm LAE}/3$.
This means that it is possible to have $N_{\rm{halos}} < N_{\rm LAE}$
and hence $\focc\equiv N_{\rm{LAE}}/N_{\rm{halos}}>1$.
We include the $1/3$ factor to account for the uncertainty in the number
density of LAEs due to cosmic variance, expecting it to be on the
same order as the dark matter halo cosmic variance shown in
Fig. \ref{fig:cosmicv0}.   Our likelihood is taken proportional to
$ \exp(-\chi_{\mathcal  M}^2/2)$, with the $\chi_{\mathcal{M}}^2$ where:

>>>>

We use halo catalogs constructed with a Bound-Density-Maxima (BDM)
algorithm. 
The catalogs were obtained from the publicly available Multidark
database  \footnote{\url{http://www.multidark.org/MultiDark/}}
\citep{MultiDark}. 
For each  halo in the box we extract its comoving position and mass.  
We focus our work on halos more massive than $1.5\times
10^{9}$\hMsun\ resolved with at least  $40$ particles 
to guarantee a well behaved halo mass function. 
We do not take into account sub-halos.

@@

The MCMC exploration is done using a total of 24 seeds and 400
iterations (9600 models) to sample the posterior  probability distribution function 
($P(\mathcal{M}|\mathrm{observations}$) based on the Angular
Correlation Function (ACF). We put a flat prior on $\log M_{\rm min}$ and $\log \mmax$ between
$9.8$ up to $13.4$, corresponding to the halo mass range of
the simulation at $z=3$.
We restrict the selection to models that give a minimal number density
$N_{\rm{halos}}>N_{\rm LAE}/3$.
This means that it is possible to have $N_{\rm{halos}} < N_{\rm LAE}$
and hence $\focc\equiv N_{\rm{LAE}}/N_{\rm{halos}}>1$.
We include the $1/3$ factor to account for the uncertainty in the number
density of LAEs due to cosmic variance, expecting it to be on the
same order as the dark matter halo cosmic variance shown in
Fig. \ref{fig:cosmicv0}.   Our likelihood is taken proportional to
$ \exp(-\chi_{\mathcal  M}^2/2)$, with the $\chi_{\mathcal{M}}^2$ where:
